Hydras \& Co.

### 2022-09-01 doc/hydras.tex
On gaia (#131)
* minor change

* experiments on a type of ordinal notation (draft)

* try to fix an issue (coq 8.14)

* try to fix an issue (coq 8.13)

* restrict to MathComp 1.13.0 and later in opam and ci

* small simplification

* slightly improve mathComp code

Co-authored-by: Karl Palmskog <palmskog@gmail.com>
new part in the book

[John Coltrane]
\end{quote}
\mbox{}
\newpage
\newpage
% \mbox{~}
\thispagestyle{empty}
\label{watercolor}
 {\centering
      \includegraphics[width=13cm]{blue-hydra.jpg}
      \centerline{\emph{``The blue hydra'': Watercolor  by Pierrette Cassou-Noguès}}
}

@@

\include{part-hydras-intro}
\include{hydra-chapter}
\include{ordinal-chapter}
\include{epsilon0-chapter}
\include{ks-chapter}
\include{large-sets-chapter}
\include{gaia-chapter}
\include{schutte-chapter}
\include{Gamma0-chapter}
\include{chapter-primrec}

>>>>

[John Coltrane]
\end{quote}
\vspace{6pt}
\mbox{}
\label{watercolorgray}
 {\centering
      \includegraphics[width=12cm]{hydre-pierrette.jpg}
      \centerline{\emph{``The hydra in black and white'': Watercolor  by Pierrette Cassou-Noguès}}
}
\newpage
\newpage
% \mbox{~}
\thispagestyle{empty}
\label{watercolor}
 {\centering
      \includegraphics[width=13cm]{blue-hydra.jpg}
      \centerline{\emph{``The blue hydra'': Watercolor  by Pierrette Cassou-Noguès}}
}

@@

\include{part-hydras-intro}
\include{hydra-chapter}
\include{ordinal-chapter}
\include{epsilon0-chapter}
\include{ks-chapter}
\include{large-sets-chapter}
\include{gaia-chapter}
\include{schutte-chapter}
\include{Gamma0-chapter}

\part{Ackermann, G\"{o}del, Peano\,\dots}
This part contains comments, example  and exercises about Russel O'Connor's work on G\"{o}del's first incompleteness theorem.  This work is maintained by Coq community~\cite{CoqCommunity} volunteers: (projects Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}).

Some changes are made to the aforementionned libraries, mainly because of the recent evolution of coq and its libraries. Nevertheless, the definitions, lemmas and theorems of the original contribution have been kept in this new release.

\emph{\color{red!80}This maintenance job has just started, ant will probably be long to complete. Help will be welcome!}

\include{chapter-primrec}
